%-------------------------------------------------------------------------------
% Dharani N - Software Engineer 
%-------------------------------------------------------------------------------
\documentclass[letterpaper,11pt]{article}

\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage[T1]{fontenc}
\usepackage{tabularx}
\usepackage{xcolor}

% ---------- Page geometry ----------
\addtolength{\oddsidemargin}{-0.55in}
\addtolength{\evensidemargin}{-0.55in}
\addtolength{\textwidth}{1.1in}
\addtolength{\topmargin}{-0.7in}
\addtolength{\textheight}{1.45in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% ---------- Section formatting ----------
\titleformat{\section}{
  \vspace{-6pt}\scshape\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

\pdfgentounicode=1

% ---------- Custom commands ----------
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-6pt}
}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.2in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-4pt}}

%-------------------------------------------------------------------------------
\begin{document}

% ---------- HEADING ----------
\begin{center}
    {\Huge \scshape Dharani N} \\ \vspace{5pt}
    \small
    Erode, Tamil Nadu, India \\ \vspace{2pt}
    6381443466 \quad $\diamond$ \quad
    \href{mailto:dharanin3466@gmail.com}{dharanin3466@gmail.com} \\ \vspace{2pt}
    \href{https://www.linkedin.com/in/dharani-n-717432269}{linkedin.com/in/dharani-n} \quad $\diamond$ \quad
    \href{https://github.com/dharani2005-long}{github.com/dharani2005-long}
\end{center}

% ---------- SUMMARY ----------
\section{Summary}
\small{Aspiring Software Engineer with a strong foundation in Java, Object-Oriented Programming, Data Structures, and full-stack web development. Skilled in building backend applications and REST APIs using Spring Boot, Hibernate, JDBC, and SQL. Passionate about problem solving and writing clean, maintainable, and scalable code.}
\vspace{-4pt}

% ---------- SKILLS ----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
    \textbf{Programming Languages}: Java, C, SQL \\ \vspace{2pt}
    \textbf{Web Technologies}: HTML, CSS, JavaScript, Bootstrap \\ \vspace{2pt}
    \textbf{Frameworks \& Libraries}: Spring, Spring Boot, Hibernate, JDBC \\ \vspace{2pt}
    \textbf{Databases}: SQL, MySQL \\ \vspace{2pt}
    \textbf{Tools \& Platforms}: Git, GitHub, REST APIs \\ \vspace{2pt}
    \textbf{Concepts}: Data Structures, OOPS, DBMS, Web Security (OWASP)
  }}
\end{itemize}
\vspace{-12pt}

% ---------- EDUCATION ----------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {K.S.R. College of Engineering}{Erode, Tamil Nadu}
    {B.E. Mechanical Engineering --- CGPA: 7.8 / 10}{2021 -- 2025}
  \resumeSubheading
    {Government Hr. Sec. School, Minnapalayam}{Tamil Nadu}
    {Class XII, State Board --- 63.8\% \quad | \quad Class X, State Board --- 60\%}{}
\resumeSubHeadingListEnd

% ---------- PROJECTS ----------
\section{Projects}
\resumeSubHeadingListStart

  \resumeProjectHeading
    {\textbf{Smart Parking Management System} $|$ \emph{Java, Spring Boot, Hibernate, JDBC, MySQL, REST API}}{}
    \resumeItemListStart
      \resumeItem{Built a full-stack smart parking application using \textbf{Spring Boot}, \textbf{Hibernate ORM}, and \textbf{MySQL} that tracks real-time slot availability and lets users search and book parking slots, with a responsive front-end in HTML, CSS, and JavaScript.}
      \resumeItem{Designed \textbf{RESTful APIs} for slot allocation, booking, and CRUD operations, and used JDBC and Hibernate for efficient, transaction-safe database access.}
      \resumeItem{Implemented role-based authentication (Admin / User), automated slot-release logic, and server-side input validation following OWASP security best practices.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{Smart Inventory Prediction System} $|$ \emph{Java, Spring Boot, Hibernate, JDBC, MySQL, REST API}}{}
    \resumeItemListStart
      \resumeItem{Developed a full-stack inventory management application with \textbf{Spring Boot} REST APIs, \textbf{Hibernate}, and a \textbf{MySQL} database to track stock levels, sales, and supplier records.}
      \resumeItem{Implemented demand-prediction and automated reorder logic that analyzes historical usage to forecast low-stock items and trigger restock alerts.}
      \resumeItem{Built CRUD operations, role-based access control, and an interactive dashboard using HTML, CSS, and JavaScript to visualize inventory trends.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{Personal Portfolio Website} $|$ \emph{HTML, CSS, JavaScript, Bootstrap}}{\href{https://dharani2005-long.github.io/Personal-Portfolio-Dharani-N/Portfolio}{Live Demo}}
    \resumeItemListStart
      \resumeItem{Designed and developed a responsive personal portfolio website to showcase projects, skills, and achievements across multiple screen sizes.}
      \resumeItem{Deployed the website on \textbf{GitHub Pages} for public access.}
    \resumeItemListEnd

\resumeSubHeadingListEnd

% ---------- EXPERIENCE ----------
\section{Internship}
\resumeSubHeadingListStart
  \resumeSubheading
    {SAN Technovation}{July 2024}
    {Design Intern}{}
    \resumeItemListStart
      \resumeItem{Worked with AutoCAD and Creo for 2D drafting and part modeling, strengthening analytical and structured problem-solving skills.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

% ---------- CERTIFICATIONS ----------
\section{Certifications}
\resumeSubHeadingListStart
  \small{\item{
    \textbf{Introduction to HTML \& CSS} --- GUVI \\ \vspace{2pt}
    \textbf{Rapid Manufacturing} --- NPTEL
  }}
\resumeSubHeadingListEnd
\vspace{-12pt}

% ---------- ACHIEVEMENTS ----------
\section{Achievements \& Activities}
\begin{itemize}[leftmargin=0.2in, itemsep=-2pt]
  \small
  \item 4-Star rating in C Programming on HackerRank.
  \item Solved multiple Data Structures \& Algorithms problems on LeetCode using Java.
  \item Participated in the Smart India Hackathon (SIH) and presented a technical paper at an inter-college event.
\end{itemize}

\end{document}